Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-21 chap-intro.tex
Document numbering better

\paragraph{Numbering}
We number tables and figures per-chapter with a shared counter. For instance,
\cref{fig:measurements-overview} is the first figure in \cref{sec:evaluation},
followed by \cref{table:performance}.

Similarly, we number definitions, remarks, examples and all sorts of theorems
per-chapter with counters including section numbers. For
instance, \cref{def:inc-semantics} is the first definition in
\cref{ch:derive-formally}, followed by \cref{thm:derive-correct}, and they both
appear in \cref{sec:correct-derive}.

All such references are hyperlinked in electronic versions of this thesis.

>>>>

\paragraph{Numbering}
We use numbering and hyperlinks to help navigation; we explain our conventions
to enable exploiting them.

To simplify navigation, we number all sorts of ``theorems'' (including here
definitions, remarks, even examples or notations)
per-chapter with counters including section numbers. For
instance, \cref{def:inc-semantics} is the first such item in
\cref{ch:derive-formally}, followed by \cref{thm:derive-correct}, and they both
appear in \cref{sec:correct-derive}. And we can be sure that \cref{lem:derive-typing}
comes after both ``theorems'' because of its number, even if they are of different sorts.

Similarly, we number tables and figures per-chapter with a shared counter. For instance,
\cref{fig:measurements-overview} is the first figure or table in \cref{sec:evaluation},
followed by \cref{table:performance}.

To help reading, at times we will repeat or anticipate statements of
``theorems'' to refer to them, without forcing readers to jump back and forth.
We will then reuse the original number.
For instance \cref{sec:correct-derive} contains a copy of \cref{slogan:derive}
with its original number.

For ease of navigation, all such references are hyperlinked in electronic
versions of this thesis, and the table of contents is exposed to PDF readers via
PDF bookmarks.
